Vulnerability Analysis of Container Images in Neuroimaging

### 2020-06-03 paper.tex
comment changes 2

However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. The security
of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Besides web applications, containers are also popularly used for scientific computing
and data science in neuroscience. In fact, Singularity was developed for scientific applications
by keeping the focus on HPC environments. This popularity of containers leads us to the
primary research question of this work: \textit{what is the current security state of
container images that are deployed on HPC clusters?}

@@

\tristan{The above text contains true statements, but they are not organized 
to introduce the paper correctly. It should be rewritten according to the following logic:
\begin{itemize}
	\item Containers are popular in various scientific fields, in particular to run Big Data analyses on HPC clusters. Mention that neuroimaging is our particular focus, although this work is of general interest.
	\item However, deploying container images on clusters raises security issues. Some security issues that could possibly lead to privilege escalation, DoS or information leak. Some
	security issues are related to the architecture of container systems (Docker) but have been largely solved by Singularity.
	\item Here we are interested in image vulnerabilities [explain research questions as you did]
	\item [introduce paper outline as done]
\end{itemize}}

\textit{RQ1:} Are vulnerabilities present inside container images that are
deployed on HPC clusters?

@@

To answer those questions, we take an example of neuroscience field where
containers are used on Compute Canada HPC cluster.

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Also, Singularity came up with Stools \href{https://github.com/singularityhub/stools}{(https://github.com/singularityhub/stools)}, which can be used for scanning Singularity images
for security and quality checks.
Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
neuroimaging as an example.

This paper is organized as follows: in the next section, we provide description
of materials and methods which summarize our four main experiments. We also explain
scanning tools that we use for scanning container images to report
vulnerabilities. The next section of this paper provides the results, where we
present a number of existing vulnerabilities in the container images
used for data analysis on shared HPC clusters. We then proceed in the following section with 
discussion and analysis of these results, where we provide more insight into the problems that 
we faced while conducting these experiments. Finally, we conclude this paper by proposing some
particular rules that can be followed to secure container images for use in clusters.

@@

\change{This study involves several image scanning experiments. To begin with,
we scan the images as is to report the existing vulnerabilities
inside the images. Updating these images is likely to play a role in vulnerabilities. Therefore, we
update the images and then rescan all these
images.
Subsequently, we shrink the size of the images
meaning that remove unnecessary packages from the images to see the effect on the number of
vulnerabilities in the images.
Lastly, we update and shrink the image size together and then
rescan for the vulnerabilities.

In this section, we first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we provide more insight
into the container images and the image scanners that we used in our study.
The image scanners are going to report different results due to different Linux
distributions/releases, which have different vulnerability data. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.}

@@

\tristan{This sub-section has a lot of boilerplate material. It should be summarized.}

Container tools are capable of packing and running an application in an isolated environment that has
the application's dependencies,
required libraries, and configuration files for the
application to function properly.

@@

Docker uses a client-server architecture, where client, containers, communicate to
the server, Docker Daemon, which is also known as the Docker engine.
Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

%consists of the following three main components: 
%
%\textit{Docker Daemon:} It acts as a server. It is
%a long-running process that manages all Docker images, containers, storage volumes, and networks.
%
%\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
%to talk to the \textit{Docker Daemon}.
%
%\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
%Docker runs a software, \textit{Docker daemon}, on the host machine.
It runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

@@

\change{Container image scanners can be broadly categorized into static and dynamic
scanners. Static scanning performs analysis on a image without running it
as a container. Therefore, package manager, which is a executable file,
cannot be used to extract required data while statically extracting image data.
Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
parsed to get information about OS distribution.
Whereas in dynamic scanning, a container is deployed from the image first and then
package manager of the image is executed inside the container to collect required data.}

@@

\change{We used four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
images while Stools supports Singularity. Vuls support both static as well as dynamic
scanning till version 0.9.5, however, in our experiments we used it dynamically.
On the contrary, the others
are static scanners.} To avoid discrepancies, we froze the vulnerability
databases for these scanners on September 25, 2019.

\tristan{The scanner descriptions need to be streamlined. They are quite verbose and not very consistent for now.}

@@

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
%\begin{comment}
%Anchore is a set of tools, which users can
%employ for scanning container images and applying custom policies to them.
%It provides visibility and transparency of the container environment.
%\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
%\begin{comment}
%Anchore offers services in two ways: Anchore Engine and Anchore
%Command Line Interface (CLI). Anchore Engine is available as a Docker
%image, which is available on Docker Hub. Anchore Engine CLI provides
%command line interface in addition to Anchore Engine REST API. 
%\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
version 0.0.11.

@@

\begin{figure}
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan mode.
The Fast scan is performed without root privileges, whereas a fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. Fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. The Deep scan uses
root privileges for scanning and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.

@@

\change{In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
last updated on 2019-09-18. We performed
scanning on 2019-09-25. So, it means that Clair Scanner's database was already
old by one week.}

@@

\change{Image scanners report vulnerabilities differently depending on the Linux release types.
Therefore, we provide an overview of these Linux releases by taking an example. 
BIDS app and Boutiques images in our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution have different releases in general. Here, we take Ubuntu as an example
to discuss different releases and their vulnerability databases. We took Ubuntu's example
because mostly images in our experiments have this distibution.} In the case of Ubuntu, release
can be of two types: Regular or Long Term Support (LTS).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

\change{If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script 
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

@@

Finally, we combine both update and size reduction process
to lessen the number of vulnerabilities.
Therefore, in this process we first update all the packages in the image and then deletes
the unnecessary packages. For this process we used the same scripts that
we used for earlier experiments.}

@@

Table~\ref{table1} shows the number of vulnerabilities present in the images,
which are detected by the scanners.
\tristan{You should refer to tables in the order they are presented (1
first, then 2). Tables should also be located next to their reference.}
It is important to note that results have major discrepancies.
The Jaccard coefficient of Anchore with both Clair and Vuls is 0.59,
whereas Vuls and Clair have 0.83.

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
%\begin{table*}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\textwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c |c},
%	table head =Image Labels &{Image names} & {OS} & {Anchore} & {Clair} & {Vuls}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table1}Existing number of Vulnerabilities}
%\end{table*}

@@

\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

\begin{figure*}[t]
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
      \end{figure*}

\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Number of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

When we add all regions of Venn diagram
we get total 20050 vulnerabilities in BIDS apps and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 reported only by Clair, and 325 detected only by Vuls.

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.

@@

\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. \change{The reasons of Clair showing
false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
However, we did not receive any reply from developers.}

@@

\textbf{CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		However, if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

@@

Our third experiment involves deleting unnecessary packages from the images.
\change{We did this experiment on five images because the reduction process may take
several hours because it requires 
a pipeline to run in the image, which takes time. We noticed that
after the size reduction process, the scanning results deviate a little from our initial expectation.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, deleting more packages reduces more vulnerabilities. 
For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.} 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

@@

As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
already reached end-of-life and are
no longer getting updates. Furthermore, the minimization of images is a time consuming process. As we have to run
the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, maybe it runs a particular
branch of the program. So there should be some kind of coverage measurement.

\tristan{You should comment on the important number of vulnerabilities found in the images overall.}

\tristan{Mention software not installed thorugh the package manager.}

@@

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number. However, for some
vulnerabilities there are no fixes available yet so the images cannot 
be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
always true. It depends on two factors: kind and the number of packages that we are
deleting. Therefore, we conclude this paper by suggesting some particular rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
\newline 3. Mind your base OS image.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Mind your GitHub/DockerHub credentials.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images.

@@

\tristan{future work}

>>>>

However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. The security
of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Containers are popular in various scientific fields, in particular to run Big Data analyses
on HPC clusters. 
However, deploying Docker container images on clusters raises security issues. Some security issues 
that could possibly lead to privilege escalation, DoS or information leak. Some
security issues are related to the architecture of Docker but have been 
largely solved by Singularity.
In fact, Singularity was developed for scientific applications
by keeping the focus on HPC environments. Although, this work is of general interest,
our particular focus in this paper is neuroimaging as containers are popularly used for scientific computing and data science
in neuroscience.
This popularity of containers in neuroscience leads us to the
primary research question of this work: \textit{what is the current security state of
neuroimaging container images that are deployed on HPC clusters?}

@@

\textit{RQ1:} Are vulnerabilities present inside neuroimaging container images that are
deployed on HPC clusters?

@@

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Zerouali et al. in~\cite{zerouali2019relation} studied severity vulnerabilities and bugs in Docker 
containers due to outdated packages.

There are various image scanners available for scanning Docker images, for
instance Anchore, CoreOS's Clair, etc.
However, these scanners cannot be used to scan Singularity images due to different image formats.
Therefore, Singularity came up with Stools \href{https://github.com/singularityhub/stools}{(https://github.com/singularityhub/stools)}, which can be used for scanning Singularity images
for security and quality checks.

This paper is organized as follows: in the next section, we provide description
of materials and methods which summarize our experiments. We also explain different
image scanners used to report
vulnerabilities in container images. The next section of this paper provides the results, where we
present a number of existing vulnerabilities in the container images
used for data analysis on shared HPC clusters. We then proceed in the following section with 
discussion and analysis of these results, where we provide more insight into the problems that 
we faced while conducting these experiments. We also propose some
particular rules that can be followed to secure container images. Finally, conclusions are drawn
in the last section of the paper.

@@

This study involves several image scanning experiments. To begin with,
we scan the images as is to report the existing vulnerabilities
inside the images. Updating these images is likely to play a role in vulnerabilities. Therefore, we
update the images and then rescan all these
images.
Subsequently, we shrink the size of the images
meaning that remove unnecessary packages from the images to see the effect on the number of
vulnerabilities in the images.
Lastly, we update and shrink the image size together and then
rescan for the vulnerabilities.

In this section, we first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we provide more insight
into the container images and the image scanners that we used in our study.
The image scanners are going to report different results due to different Linux
distributions/releases, which have different vulnerability data. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.

@@

In this paper, we consider two popular container tools i.e Docker and Singularity because
neuroimaging uses images from these two tools.
%Container tools are capable of packing and running an application in an isolated environment that has
%the application's dependencies,
%required libraries, and configuration files for the
%application to function properly.

@@

%Docker uses a client-server architecture, where client, containers, communicate to
%the server, Docker Daemon, which is also known as the Docker engine.
%Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

%consists of the following three main components: 
%
%\textit{Docker Daemon:} It acts as a server. It is
%a long-running process that manages all Docker images, containers, storage volumes, and networks.
%
%\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
%to talk to the \textit{Docker Daemon}.
%
%\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
%Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker Engine, which runs as root, is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

@@

Container image scanners can be broadly categorized into static and dynamic
scanners. Static scanning performs analysis on a image without running it
as a container. Therefore, package manager, which is a executable file,
cannot be used to extract required data while statically extracting image data.
Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
parsed to get information about OS distribution.
Whereas in dynamic scanning, a container is deployed from the image first and then
package manager of the image is executed inside the container to collect required data.

@@

We used four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
images while Stools supports Singularity. Vuls support both static as well as dynamic
scanning till version 0.9.5, however, in our experiments we used it dynamically.
On the contrary, the others
are static scanners. To avoid discrepancies, we froze the vulnerability
databases for these scanners on September 25, 2019.

@@

Anchore is an end-to-end, open-source container security platform. It
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
%\begin{comment}
%Anchore is a set of tools, which users can
%employ for scanning container images and applying custom policies to them.
%It provides visibility and transparency of the container environment.
%\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
%\begin{comment}
%Anchore offers services in two ways: Anchore Engine and Anchore
%Command Line Interface (CLI). Anchore Engine is available as a Docker
%image, which is available on Docker Hub. Anchore Engine CLI provides
%command line interface in addition to Anchore Engine REST API. 
%\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Database
version 0.0.11.

@@

\begin{figure}[!ht]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
It offers both static and dynamic scanning. In our experiments, we used
it to dynamically scan containers.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan mode.
%The Fast scan is performed without root privileges, whereas a fast root scan is
%performed with root privileges. The latter also uses checkrestart utility to 
%detect processes that are updated but not yet restarted because if they are not
%restarted, updates are not effective. Fast root scan also detects these
%processes. Both fast scan and fast root scan are performed offline without Internet
%access, and put almost no load on the scan target server. The Deep scan uses
%root privileges for scanning and is used to get a more detailed scan. It checks
%changelogs, which puts more load on the target server.

@@

In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
last updated on 2019-09-18. We performed
scanning on 2019-09-25. So, it means that Clair Scanner's database was already
old by one week.

@@

Image scanners report vulnerabilities differently depending on the different Linux release types.
Therefore, we provide an overview of these Linux releases and scanners re. 
BIDS app and Boutiques images in our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution have different releases in general. Here, we take Ubuntu's example
to discuss different releases and their vulnerability databases. We took Ubuntu's example
because mostly images in our experiments have this distibution. However, other distributions also have
similar release trend. In the case of Ubuntu, release
can be of two types: Regular or Long Term Support (LTS).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script 
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

@@

Finally, we combine both update and size reduction process
to lessen the number of vulnerabilities.
Therefore, in this process we first update all the packages in the image and then deletes
the unnecessary packages. For this process we used the same scripts that
we used for earlier experiments.

@@

Table~\ref{table1} shows the number of vulnerabilities present in the images,
which are detected by the scanners.
It is important to note that results have major discrepancies. In particular,
Anchore reports far more different results than Vuls and Clair resulting in 
the Jaccard coefficient of 0.59 with both,
whereas Vuls and Clair share more common vulnerabilities resulting to the Jaccard coefficient of 0.83.

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains more packages and hence report more vulnerabilities.
We also analyzed that out of the total Docker images scanned in our experiment, Debian reported more critical vulnerabilties than others, reaching
up to 180.
%\begin{table*}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\textwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c |c},
%	table head =Image Labels &{Image names} & {OS} & {Anchore} & {Clair} & {Vuls}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table1}Existing number of Vulnerabilities}
%\end{table*}

@@

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
      \end{figure*}

\begin{figure}[!ht]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

%\begin{figure*}[b]
%        {\includegraphics[width=\textwidth]
%        {Figures/vulnwithupdate.pdf}}
%        \caption{\label{fig:graph2} Number of vulnerabilities before and
%        after update of the images}
%      \end{figure*}

@@

Figure~\ref{fig:venn} represents the number of common and different vulnerabilities
that are shown by scanners.
When we add all regions of Venn diagram
we get total 20050 vulnerabilities in BIDS apps and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 reported only by Clair, and 325 detected only by Vuls.

@@

\begin{figure*}[!ht]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Number of vulnerabilities before and
        after update of the images}
      \end{figure*}

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.

@@

\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. The reasons of Clair showing
false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}

@@

\textbf{CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		However, if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04. We reported this bug as well through slack
		channel.

@@

Our third experiment involves deleting unnecessary packages from the images.
We did this experiment on five images because the reduction process may take
several hours because it requires 
a pipeline to run in the image, which takes time. We noticed that
after the size reduction process, the scanning results deviate a little from our initial expectation.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, deleting more packages reduces more vulnerabilities. 
For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

@@

As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
so many are critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
already reached end-of-life and are
no longer getting updates. Furthermore, the minimization of images is a time consuming process. As we have to run
the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, maybe it runs a particular
branch of the program. So there should be some kind of coverage measurement.
Besides this, as scanners report vulnerabilities according to the versions of the installed packages,
they are likely to miss packages that are not installed using package manager. 
Therefore, we suggest some particular rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
\newline 3. Choose your base OS image wisely.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Protect your GitHub/DockerHub credentials because if automated builds is set up
in Docker Hub, it can automatically build images from external repositories, for instance GitHub.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images. Docker Content Trust (DCT) provides ability to digitally sign
images to verify the integrity of the images.

@@

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number. However, for some
vulnerabilities there are no fixes available yet so the images cannot 
be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
always true. It depends on two factors: kind and the number of packages that we are
deleting.

@@
